---
title: "Augmented Testing Study Analysis"
author: "Andreas Bauer"
date: "2024-01-02"
execute:
  echo: true
  warning: false
fig-dpi: 300
format:
  html:
    fig-width: 8
    fig-height: 6
---

## Introduction

TBD

## Load libraries

```{r}
library(tidyverse)
```

## Data

First, load the data from the table of results.

```{r load-data}
df_raw <- read.csv(file = "data/at-study.csv", header = TRUE, sep = ",", fileEncoding = "UTF-8-BOM")
```

### Cleanup and transform data

To work with the raw data we transform into the following more convenient format:

| Column | Description | Type |
|---|---|---|
| `id` | The identifier of a participant | int |
| `tc` | The identifier of a test case | int |
| `tc_big` | Size of the test case.  `TRUE` for bigger and `FALSE` for smaller test cases. | Boolean |
| `treatment` | `TRUE` for Augmented Testing and `FALSE` for manual GUI testing | Boolean |
| `duration_scaled` | Duration of performing test cases (normalized) | float |

Next, we normalize the duration of performeed test cases to allow a comparison between test cases of different size.
The duration is scaled to an interval of size 1 centered around the mean value of each test case.

```{r}
df <- df_raw %>%
  pivot_longer(
    cols = c(matches("TC._treatment"), matches("TC._seconds$")),
    names_to = c("tc", ".value"), names_pattern = "TC(.)_(.*)"
  ) %>%
  select("ID", "tc", "treatment", "seconds") %>%
  mutate(
    treatment = (treatment == "A"),
    tc_big = (tc %in% c(3, 4, 7, 8))
  )

head(df)
```

```{r}
df <- df %>%
  group_by(tc) %>%
  mutate(
    duration_scaled = (seconds - mean(seconds)) / (max(seconds) - min(seconds))
  )
```


